A New Metropolis-Hastings Test for Fast Minibatch MCMC Inference and Optimization

### 2016-05-16 nips_2016.tex
add the finalized figs for exp2

From the figures above, we find that with the help of our mini-batch MH testing we can obtain the sampled distribution which are very close to target one. We feature draw our estimation of standard derivation of $X_{\rm norm}$ over iterations, see Fig.~3e. We find with even constant step size, the standard derivation decreases, because the gradient of posterior distribution declines and make the scale of $\Delta'$ deminished when the sampled point is apporching MAP. Thus, the error our transition kernel will declines with even constant step size as discribed in Sect.~ 4.
\subsection{Logistic Regression}\label{ssec:logistic}
In this experiment, we use logistic regression to classify the MNIST dataset. For similification, we only train the binary classifer for digits 1 vs 7. The dataset consisted of 12007 training data and 1000 testing data. Similarly, we use random walk as the proposer. We compare our mini-batch MH testing with the adaptive mini-batch MH testing. Figure 4 shows the loglikelihood value and perdiction accuracy over training process. Since the adaptive MH testing method needs to increase the mini-batch size adaptively, we use the cumulative number of data instance each algorithm consumes as the horizontal axis.
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for logistic regression.}
\end{figure}

{\color{blue}
Daniel: TODO

@@

{\color{blue}
Daniel: TODO

For additional details, see Appendix~\ref{app:nnet}.
}

>>>>

From the figures above, we find that with the help of our mini-batch MH testing we can obtain the sampled distribution which are very close to target one. We feature draw our estimation of standard derivation of $X_{\rm norm}$ over iterations, see Fig.~3e. We find with even constant step size, the standard derivation decreases, because the gradient of posterior distribution declines and make the scale of $\Delta'$ deminished when the sampled point is apporching MAP. Thus, the error our transition kernel will declines with even constant step size as discribed in Sect.~ 4.
\subsection{Logistic Regression}\label{ssec:logistic}
In this experiment, we use logistic regression to classify the MNIST dataset. For similification, we only train the binary classifer for digits 1 vs 7. The dataset consisted of 12007 training data and 1000 testing data. Similarly, we use random walk as the proposer. We compare our mini-batch MH testing with the adaptive mini-batch MH testing. Figure 4 shows the loglikelihood value and perdiction accuracy over training process. Since the adaptive MH testing method needs to increase the mini-batch size adaptively, we use the cumulative number of data instance each algorithm consumes as the horizontal axis. We find our mini-batch MH testing can achieve the similar (or even better loglikelihood/prediction accuracy) with consuming much fewer data points. Thus, we can assert that our mini-batch MH testing is much more efficient than the adaptive one.

In this experiment, we also illustrate that by appling the temperature, we can achieve slight faster convergence than the constant temperature one.
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for logistic regression.}
\end{figure}

We use this experiment to illustarte another property of our mini-batch MH testing:

{\color{blue}
Daniel: TODO
Add the roofline description.

@@

{\color{blue}
Daniel: TODO
1) describe the data background
2) describe the SGHMC proposer, and our other hyperparams
3) show the results and analysis
For additional details, see Appendix~\ref{app:nnet}.
}
